worldmap

### 2024-11-18 analysis/figures/visualization.Rmd
Figured out the pairwise results annotation!

get_estimate <- function(metric_name, term_name){
  model_output %>% 
    filter(metric == metric_name, term == term_name) %>%
    pull(estimate_scale)
}

climate_plot <- group_slopes %>%
  filter(model_id == "climate") %>%
  ggplot(aes(y = numeric_metric, x = estimate_scale, color = term)) +
  geom_point(aes(shape = sig), size = 3) +
  #ylim(-7,7) +
  #scale_x_discrete(expand=c(0.001, 4)) +
  theme_bw() +
  theme(axis.title.y = element_blank(), legend.title = element_blank(),
        legend.position = "bottom", 
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black")
        ) +
  scale_shape_manual(values = c(1, 19), guide = "none") +
  #ggpubr::geom_bracket(data = group_slopes %>% filter(model_id == "climate"), xmin = unlist(get_estimate("CWM_diet_vunk", "Marine")), xmax = unlist(get_estimate("CWM_diet_vunk", "Terrestrial")), y.position = 11, label = "") +
  scale_y_discrete(labels = group_slopes %>% select(numeric_metric, plot_label) %>% distinct() %>% tibble::deframe(), drop = FALSE) +
  scale_color_manual(values = group_colors) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  guides(color=guide_legend(nrow=2, byrow=TRUE)) +
  xlab("temporal slope estimate")

@@

realm_plot <- group_slopes %>%
  filter(model_id == "realm") %>%
  ggplot(aes(y = numeric_metric, x = estimate_scale, color = term)) +
  geom_point(aes(shape = sig), size = 3) +
  #ylim(-7,7) +
  #scale_x_discrete(expand=c(0.001, 4)) +
  theme_bw() +
  theme(axis.title.y = element_blank(), legend.title = element_blank(),
        axis.line.y = element_blank(), axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(),
        legend.position = "bottom",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black")
        ) +
  scale_shape_manual(values = c(1, 19), guide = "none") +
  scale_color_manual(values = my_pal) +
  geom_vline(xintercept = 0, linetype = "dashed")+
  guides(color=guide_legend(nrow=2, ncol = 2, byrow=TRUE)) +
  scale_y_discrete(labels = group_slopes %>% select(numeric_metric, plot_label) %>% distinct() %>% tibble::deframe(), drop = FALSE) +
  xlab("temporal slope estimate")

>>>>

get_estimate <- function(metric_name, term_name){
  group_slopes %>% 
    filter(metric == metric_name, term == term_name) %>%
    pull(estimate_scale)
}

climate_plot <- group_slopes %>%
  filter(model_id == "climate") %>%
  ggplot(aes(y = numeric_metric, x = estimate_scale, color = term)) +
  geom_point(aes(shape = sig), size = 3) +
  geom_segment(aes(x = (get_estimate("CWM_diet_vunk", "Tropical") + 0.1), y = 11, xend = (get_estimate("CWM_diet_vunk", "Temperate") - .095)), color = "black") +
  #ylim(-7,7) +
  #scale_x_discrete(expand=c(0.001, 4)) +
  theme_bw() +
  theme(axis.title.y = element_blank(), legend.title = element_blank(),
        legend.position = "bottom", 
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black")
        ) +
  scale_shape_manual(values = c(1, 19), guide = "none") +
  #ggpubr::geom_bracket(data = group_slopes %>% filter(model_id == "climate"), xmin = unlist(get_estimate("CWM_diet_vunk", "Marine")), xmax = unlist(get_estimate("CWM_diet_vunk", "Terrestrial")), y.position = 11, label = "") +
  scale_y_discrete(labels = group_slopes %>% select(numeric_metric, plot_label) %>% distinct() %>% tibble::deframe(), drop = FALSE) +
  scale_color_manual(values = group_colors) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  guides(color=guide_legend(nrow=2, byrow=TRUE)) +
  xlab("temporal slope estimate")

@@

realm_plot <- group_slopes %>%
  filter(model_id == "realm") %>%
  ggplot(aes(y = numeric_metric, x = estimate_scale, color = term)) +
  geom_point(aes(shape = sig), size = 3) +
   geom_segment(aes(x = (get_estimate("CWM_diet_vunk", "Marine") + 0.075), y = 11, xend = (get_estimate("CWM_diet_vunk", "Terrestrial")) - 0.075), color = "black") +
  #ylim(-7,7) +
  #scale_x_discrete(expand=c(0.001, 4)) +
  theme_bw() +
  theme(axis.title.y = element_blank(), legend.title = element_blank(),
        axis.line.y = element_blank(), axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(),
        legend.position = "bottom",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(colour = "black")
        ) +
  scale_shape_manual(values = c(1, 19), guide = "none") +
  scale_color_manual(values = my_pal) +
  geom_vline(xintercept = 0, linetype = "dashed")+
  guides(color=guide_legend(nrow=2, ncol = 2, byrow=TRUE)) +
  scale_y_discrete(labels = group_slopes %>% select(numeric_metric, plot_label) %>% distinct() %>% tibble::deframe(), drop = FALSE) +
  xlab("temporal slope estimate")
